Exploration

### 2018-03-13 exploration.Rmd
needed dataframe

########
## plots
########
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=lambda.f-lambda, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black")) +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=lam.S.f-lam.S, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black")) +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=lam.U.f-lam.U, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black")) +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=lam.S>1, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=lam.S.f>1, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(lambda>1 & lambda.f>1) | (lambda<1 & lambda.f<1),
                colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(lam.S>1 & lam.S.f>1) | (lam.S<1 & lam.S.f<1),
                colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(N.S>1 & N.S.f>1) | (N.S<1 & N.S.f<1),
                colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(lam.U>1 & lam.U.f>1) | (lam.U<1 & lam.U.f<1),
                colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(N.U>1 & N.U.f>1) | (N.U<1 & N.U.f<1),
                colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(N.S.f-N.S)/N.S, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black")) +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes( fill=(Surv.S.f-Surv.S)/Surv.S, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black")) +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(Rcr.S.f-Rcr.S)/Rcr.S, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black")) +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
par(mfrow=c(3,3))
plot((lambda.f-lambda) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot((lambda.f-lambda) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot((lambda.f-lambda) ~ pOpn, data=lam.df); abline(h=0, col="red", lty=2)
plot((lambda.f-lambda) ~ pOth, data=lam.df); abline(h=0, col="red", lty=2)
plot((lambda.f-lambda) ~ pDec, data=lam.df); abline(h=0, col="red", lty=2)
plot((lambda.f-lambda) ~ pEvg, data=lam.df); abline(h=0, col="red", lty=2)
plot((lambda.f-lambda) ~ pMxd, data=lam.df); abline(h=0, col="red", lty=2)
plot(density(lambda.f-lambda)); abline(v=0, col="red", lty=2)
plot(density(lam.U.f-lam.U)); abline(v=0, col="red", lty=2)
# matplot(t(log(U.f$lam.t)), type="l", lty=1, col=rgb(0,0,0,0.1))
# matplot(t(log(apply(U.f$Nt, 3:4, sum))), type="l", lty=1, col=rgb(0,0,0,0.1))
# matplot(t(S.f$N_sim[,2:tmax]/S$N_sim[,1:(tmax-1)]), 
#         type="l", lty=1, col=rgb(0,0,0,.1))
# matplot(t(log(S.f$N_sim+1)), type="l", lty=1, col=rgb(0,0,0,0.1))

>>>>

########
## plots
########
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=lambda.f-lambda, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black")) +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=lam.S.f-lam.S, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black")) +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=lam.U.f-lam.U, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black")) +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=lam.S>1, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=lam.S.f>1, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(lambda>1 & lambda.f>1) | (lambda<1 & lambda.f<1),
                colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(lam.S>1 & lam.S.f>1) | (lam.S<1 & lam.S.f<1),
                colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(N.S>1 & N.S.f>1) | (N.S<1 & N.S.f<1),
                colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(lam.U>1 & lam.U.f>1) | (lam.U<1 & lam.U.f<1),
                colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(N.U>1 & N.U.f>1) | (N.U<1 & N.U.f<1),
                colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black"))
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(N.S.f-N.S)/N.S, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black")) +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes( fill=(Surv.S.f-Surv.S)/Surv.S, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black")) +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat)) + 
  geom_tile(aes(fill=(Rcr.S.f-Rcr.S)/Rcr.S, colour=id.inbd %in% IPM.P)) +
  scale_colour_manual(values=c(NA, "black")) +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
par(mfrow=c(3,3))
plot((lambda.f-lambda) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot((lambda.f-lambda) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot((lambda.f-lambda) ~ pOpn, data=lam.df); abline(h=0, col="red", lty=2)
plot((lambda.f-lambda) ~ pOth, data=lam.df); abline(h=0, col="red", lty=2)
plot((lambda.f-lambda) ~ pDec, data=lam.df); abline(h=0, col="red", lty=2)
plot((lambda.f-lambda) ~ pEvg, data=lam.df); abline(h=0, col="red", lty=2)
plot((lambda.f-lambda) ~ pMxd, data=lam.df); abline(h=0, col="red", lty=2)
plot(density(lam.df$lambda.f-lam.df$lambda)); abline(v=0, col="red", lty=2)
plot(density(lam.df$lam.U.f-lam.df$lam.U)); abline(v=0, col="red", lty=2)
# matplot(t(log(U.f$lam.t)), type="l", lty=1, col=rgb(0,0,0,0.1))
# matplot(t(log(apply(U.f$Nt, 3:4, sum))), type="l", lty=1, col=rgb(0,0,0,0.1))
# matplot(t(S.f$N_sim[,2:tmax]/S$N_sim[,1:(tmax-1)]), 
#         type="l", lty=1, col=rgb(0,0,0,.1))
# matplot(t(log(S.f$N_sim+1)), type="l", lty=1, col=rgb(0,0,0,0.1))
